\Huge \scshape \fontfamily{pbk}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \large An Example of the dndbook Class

### 2021-07-11 example.tex
Added an option to prevent the automatic boldface of table first row text; default is still true.
Added the option to avoid boldface table header row in the DndAltTable
Added a "listparagraph" type that outputs a bolded title with hanging-indent text, used in class features, background options, etc

@@

>>>>

\listparagraph[6pt]{Listparagraph}
{The listparagraph format allows hanging indented lists of options, such as those
used for class features and background skill/tool proficiency options.}

\listparagraph{Listparagraph}
{The listparagraph with no vertical space after the previous paragraph.}

@@

The text in the first row of the table automatically uses boldface;
to prevent this, add ``bold=false'' to the optional parameters, for example:
\begin{lstlisting}[basicstyle=\ttfamily\small]
[header=Nice Table,bold=false]
\end{lstlisting}
